%-------------------------
% Resume in Latex
% Author : Eduard Zaynullin
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Eduard Zaynullin} \\ \vspace{1pt}
    \small +49 1515 746 01 63 $|$ \href{mailto:e.zaynullin@gmail.com}{\underline{e.zaynullin@gmail.com}} $|$ 
    \href{https://linkedin.com/in/eduard-zaynullin}{\underline{linkedin.com/in/eduard-zaynullin}}
\end{center}
%-----------OBJECTIVE-----------
\section{Objective}
\resumeItemListStart
    \resumeItem{Passionate about contributing to innovative software solutions using Golang}
    \resumeItem{Familiar with cloud-native solutions and excited to apply Golang for building scalable and efficient applications}
\resumeItemListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Solution Architect}{Jan. 2021 -- Present}
      {Delivery Hero SE}{Berlin, Germany}
%-----------Multiple Positions Heading-----------
      \resumeSubSubheading
        {Solution Architect}{Aug. 2023 - Present}
          \resumeItemListStart
            \resumeItem{Hands-on Golang development, migrating performance-critical processes from SAP to AWS cloud-native services}
            \resumeItem{Leading the architecture and design of SAP on AWS projects}
            \resumeItem{Implemented an efficient archiving solution, resulting in decreasing data volume growth from exponential to linear}
          \resumeItemListEnd
       \resumeSubSubheading
        {Technical Project Manager}{Jan. 2021 - Aug. 2023}
        \resumeItemListStart
           \resumeItem{Hands-on Golang development, implemented best practices for system design, security, scalability, and performance optimization on \textgreater20  projects}
           \resumeItem{Optimized sales order creation time by 10 times, increasing order processing capacity by 300\%}
           \resumeItem{Implemented advanced performance tuning techniques, leading to a significant 30\% decrease in HANA DB CPU load and reduced response time for critical business queries by 40\%}
        \resumeItemListEnd
%-------------------------------------------
    \resumeSubheading
      {Solution Architect}{Nov. 2017 -- Dec. 2020}
      {LeverX International}{Minsk, Belarus}
      \resumeItemListStart
        \resumeItem{Acted as an external employee of SAP headquarters, leading development and architecture on 12 successful Standard and Customer projects, both On-premise and Cloud.}
    \resumeItemListEnd

    \resumeSubheading
      {Team Lead, Development Architect}{July 2015 -- Nov. 2017}
      {RosEuroBank}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Led a development team for a bank CRM system, resulting in 10\% improved customer satisfaction and 20\% reduction in customer support response time}
        \resumeItem{Successfully integrated SAP CRM system with \textgreater10 third-party systems}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Nov. 2013 -- July 2015}
      {Technoserv Consulting}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Implemented SAP CRM for various clients, including \emph{Transaero Airlines} and \emph{PromSvyazbank}, resulting in improved customer service and a 20\% increase in customer retention.}
        \resumeItem{Implemented SAP ERP for \emph{RusHydro} hydroelectricity company, leading to improved resource management}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Nov. 2012 -- Nov. 2013}
      {Intuit}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Implemented a document management system (SAP, OpenText) for \emph{Gazprom Transgaz} company, leading to a 40\% reduction in document processing time and improved data accuracy}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Feb. 2012 -- Nov. 2012}
      {VoenTelecom}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Created 30+ custom SAP GUI reports, providing valuable insights for decision-making and process optimization}
    \resumeItemListEnd

    \resumeSubheading
      {Junior Researcher}{June 2010 -- Feb. 2012}
      {Fiber Optics Research Center}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Designed and created 3 types of fiber-optic sensors, including vibroacoustic, pressure, and temperature sensors}
    \resumeItemListEnd

    \resumeSubheading
      {Technical Support Engineer}{Apr. 2008 -- June 2009}
      {Caravan Telecom}{Moscow, Russia}
      \resumeItemListStart
        \resumeItem{Administered \textgreater1000 virtual hosting Unix servers, maintaining 99.9\% uptime}
        \resumeItem{Set up monitoring, archiving, configured network, load balancing, and disaster recovery}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Research Nuclear University "MEPhI"}{Moscow, Russia}
      {Master of physics (laser and quantum physics)}{2005 -- 2012}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Golang, ABAP, Python, SQL, PHP, HTML/CSS } \\
     \textbf{Databases}{: HANA, Oracle, MySQL, PostgreSQL, BigQuery, DynamoDB } \\
     \textbf{Cloud and Enterprise Platforms}{: AWS, Google Cloud, SAP BTP, S/4HANA, SAP ECC} \\
     \textbf{Tools}{: Git, Docker, Kubernetes (managed), Datadog, Prometheus, Grafana} \\
    }}
 \end{itemize}

%-------------------------------------------https://www.overleaf.com/project/64c8269ecd27a7cf0e6759dd
\end{document}
